\begin{center}
\Large\bfseries
Surgical Ward Clinical Handover System
\end{center}

\section*{Abstract}
A hospital is a labyrinth of paper forms and corridor communication. In order to find their way, users must use considerable effort in order to receive and transfer information. The information system SANSURGIMS aims to make it considerably easier to access this information. Through requirements analysis and system design, the student has created a system that allows clinical staff to more efficiently transfer information from one shift to the next. This not only makes their work easier but also allows them to spend more time doing their real work, taking care of patients. 

\section*{Acknowledgements}
I would like to thank the Sydney Adventist Hospital for giving me the chance to experience a living, breathing hospital setting. I would like to thank Chris Williams for making these projects possible. I would like to thank Hannah Chong for her guidance and support during my stay at the hospital. She helped me stay afloat in the sea of information that is patient care. I would like to thank Vivien Lane and Jane Gardner as well as the many other staff at the SAN that spared their time to review and guide my work. I would also like to thank Janelle Craig for helping me to settle into the SAN. I would like to thank Prof. Jon Patrick and Decler Hague for their academic support and guidance through this project. I would like to thank Prof. Jon Patrick for giving me the opportunity to work with iCIMS.
